\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-06-22 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
updating Section IV

The corresponding macroscopic dynamics governing the flow of the joint state PDF $\rho(t,\bm{\theta},\bm{\omega})$ is given by a kinetic Fokker-Planck partial differential equation (PDE)
\begin{align}
\frac{\partial \rho}{\partial t} &= - \langle \bm{\omega},\nabla_{\bm{\theta}}\rho \rangle  + \nabla_{\bm{\omega}} \cdot \left( \rho \left( \bm{M}^{-1}\bm{\Gamma}\bm{\omega} + \bm{M}^{-1}\nabla_{\bm{\theta}}V(\bm{\theta}) \right.\right.\nonumber\\
&\qquad\qquad\qquad \left.\left. +\frac{1}{2} \bm{M}^{-1}\bm{\Sigma}\bm{\Sigma}^{\top}\bm{M}^{-1} \nabla_{\bm{\omega}} \log \rho \right) \right),
\label{KineticFPK}	
\end{align}
subject to the initial condition \eqref{FPKInitCond} and the joint parameter PDF $\rho_{\text{param}}$. A direct numerical solution of this PDE initial value problem using conventional discretization (e.g., finite difference) or function approximation techniques will not be scalable in general, as explained in Sec. \ref{subsubsec:technicalchallenges}. In the next Section, we discuss how a measure-valued variational recursion proposed in our recent works \cite{caluya2019ACC,caluya2019TAC,halder2020hopfield,caluya2021TAC} can be employed to address this challenge.

@@

>>>>

The corresponding macroscopic dynamics governing the flow of the joint state PDF $\rho(t,\bm{\theta},\bm{\omega})$ is given by a kinetic Fokker-Planck partial differential equation (PDE)
\begin{align}
\frac{\partial \rho}{\partial t} &= - \langle \bm{\omega},\nabla_{\bm{\theta}}\rho \rangle  + \nabla_{\bm{\omega}} \cdot \left( \rho \left( \bm{M}^{-1}\bm{\Gamma}\bm{\omega} + \bm{M}^{-1}\nabla_{\bm{\theta}}V(\bm{\theta}) \right.\right.\nonumber\\
&\qquad\qquad\qquad \left.\left. +\frac{1}{2} \bm{M}^{-1}\bm{\Sigma}\bm{\Sigma}^{\top}\bm{M}^{-1} \nabla_{\bm{\omega}} \log \rho \right) \right),
\label{KineticFPK}	
\end{align}
subject to the initial condition \eqref{FPKInitCond} and the joint parameter PDF $\rho_{\text{param}}$. A direct numerical solution of this PDE initial value problem using conventional discretization (e.g., finite difference) or function approximation techniques will not be scalable in general, as explained in Sec. \ref{subsubsec:technicalchallenges}. In the next Section, we discuss how a measure-valued variational recursion proposed in our recent works \cite{caluya2019ACC,caluya2019TAC,halder2020hopfield,caluya2021TAC,caluya2021reflected} can be employed to address this challenge.

@@

\bibitem{caluya2020reflected}
K.F. Caluya, and A. Halder,``Reflected Schr$\backslash$" odinger Bridge: Density Control with Path Constraints", \emph{American Control Conference}, 2021.
